Pigeons.jl: Distributed sampling from intractable distributions

### 2024-03-23 paper/examples.tex
use paper folder
First updates based on reviewer comments
Update examples.tex

\section{Examples}
In this section we present a set of minimal examples 
that demonstrate how to use Pigeons.jl for sampling. 
For further reading, we also direct readers to our growing list of examples, which can be found at 
\url{https://github.com/Julia-Tempering/Pigeons.jl/tree/main/examples}.
We begin by installing the latest official release of Pigeons.jl: 
\begin{lstlisting}[language = Julia]
using Pkg; Pkg.add("Pigeons")
\end{lstlisting}

@@

\begin{figure}[t]
    \centering 
    \includegraphics[width=0.5\textwidth]{img/coinflip_posterior.pdf}
    \caption{Posterior distribution for the model given by \cref{eq:coinflip} 
    with $n=100,000$ coin flips and $y=50,000$ observed heads, 
    estimated using $2^{17}$ samples from Pigeons.jl. 
    We present the pairwise plot for $p_1$ and $p_2$, as well as the estimated 
    densities of the marginal of the posterior for each of the two parameters.
    Note that because the model is non-identifiable, as we collect more data the 
    posterior distribution concentrates around the curve $p_1 p_2 = 0.5$, instead 
    of a single point, assuming that the true probability of observing heads 
    is 0.5.}
    \label{fig:coinflip_posterior}
\end{figure}

@@

\begin{figure*}[t]
    \centering
    \begin{subfigure}{0.45\textwidth}
      \centering
      \includegraphics[width=\textwidth]{img/trace_density_plots_pt.pdf}
    \end{subfigure}
    \begin{subfigure}{0.45\textwidth}
      \centering
      \includegraphics[width=\textwidth]{img/trace_density_plots_single_chain.pdf}
    \end{subfigure}
    \caption{
        Trace-plots for the first parameter, $p_1$, in the 
        non-identifiable coinflip Turing model.
        \textbf{Left:} Samples from Pigeons.jl using PT with 10 chains. Note that the 
        trace-plot indicates fast mixing/exploration across the state space.
        \textbf{Right:} Single-chain Markov chain Monte Carlo. Note that the 
        trace-plot explores the state space much more slowly when we do not use PT.
    }
    \label{fig:trace_density_plots}
\end{figure*}

>>>>

\section{Examples}
In this section we present a set of minimal examples 
that demonstrate how to use Pigeons.jl for sampling. 
For further reading, we also direct readers to our growing list of examples, which can be found at 
\url{https://github.com/Julia-Tempering/Pigeons.jl/tree/main/examples}.
\NS{Add InferenceHub description and link.}

\medskip
We begin by installing the latest official release of Pigeons.jl: 
\begin{lstlisting}[language = Julia]
using Pkg; Pkg.add("Pigeons")
\end{lstlisting}

@@

\begin{figure}[t]
    \centering 
    \includegraphics[width=0.5\textwidth]{../img/coinflip_posterior.pdf}
    \caption{Posterior distribution for the model given by \cref{eq:coinflip} 
    with $n=100,000$ coin flips and $y=50,000$ observed heads, 
    estimated using $2^{17}$ samples from Pigeons.jl. 
    We present the pairwise plot for $p_1$ and $p_2$, as well as the estimated 
    densities of the marginal of the posterior for each of the two parameters.
    Note that because the model is non-identifiable, as we collect more data the 
    posterior distribution concentrates around the curve $p_1 p_2 = 0.5$, instead 
    of a single point, assuming that the true probability of observing heads 
    is 0.5.}
    \label{fig:coinflip_posterior}
\end{figure}

@@

\begin{figure*}[t]
    \centering
    \begin{minipage}{0.45\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../img/trace_density_plots_pt.pdf}
    \end{minipage}
    \begin{minipage}{0.45\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../img/trace_density_plots_single_chain.pdf}
    \end{minipage}
    \caption{
        Trace-plots for the first parameter, $p_1$, in the 
        non-identifiable coinflip Turing model.
        \textbf{Left:} Samples from Pigeons.jl using PT with 10 chains. Note that the 
        trace-plot indicates fast mixing/exploration across the state space.
        \textbf{Right:} Single-chain Markov chain Monte Carlo. Note that the 
        trace-plot explores the state space much more slowly when we do not use PT.
    }
    \label{fig:trace_density_plots}
\end{figure*}
